\documentclass[10pt,a4paper]{article}

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[unicode]{hyperref}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{\textbf{[[ #1 ]]}}}
\usepackage{courier}

\begin{document}
\noindent\textbf{Documentation of Project Implementation for IPP 2019/2020\\
Name and surname: Pavel Yadlouski\\
Login: xyadlo00\\}

\section{Interpret}
\subsection{Script composition}

Interpret comprises from managing script \texttt{interpret.py} and package that
provides backend functionality of interpret. In this package there are 4 other
modules: \texttt{opcode.py}, \texttt{frames.py}, \texttt{errors.py}, 
\texttt{other\_functions.py}. 

\subsection{Managing script}

Managing script contains two functions (\texttt{main} and \texttt{process\_xml}),
which are called in \textit{if} statement in following order: \texttt{main} 
$\rightarrow$ \texttt{proces\_xml}. In both functions exceptions can be raised 
(return codes and resolved through exceptions), so calls of this functions are 
in \textit{try} block followed by a series of \textit{except} blocks in which 
all possible errors are processed.

\texttt{main} function engaged in processing of input parameters. It checks if 
\texttt{-{}-source} and/or \texttt{-{}-input} are set and, if set, then if the
their values are correct. In case the parameter \texttt{-{}-help} is present,
then check if any other parameter is not used and writes description of script.

\subsection{Modules in package}

Interpret package contains 4 modules (\texttt{opcodes.py, other\_functions.py, 
frames.py, errors.py}) for helding different parts in interpret.  

\subsubsection{Operation codes (\texttt{opcodes.py})}

In this module all available operation codes are implemented. This functions
use secondary function to simplify implementation. Also any error that may occur 
in this functions are raised directly from secondary functions called in current 
function of operation code.  

\subsubsection{Secondary functions (\texttt{other\_functions.py})}

This module is made to simplify implementation of operation codes, to separate 
routine and avoid repetitive work such as getting name of variable and frame, 
then extracting this variable from given frame with corresponding checks. For 
example there is function \texttt{check\_math}. This function validate arguments 
for mathematical instructions. Mathematical function have common way of checking 
arguments, such as checking types of input arguments. So, all necessary 
functionality for those operation code is present in this function. Only 
function for handling \texttt{IDIV} function has a little extension for avoiding 
zero division error. Also function function \texttt{CONCAT} has generally 
similar validate. So \texttt{check\_math} also used in this function, but checks 
for string type.

This implementation helped my keep implementation of operation codes simple enough 
and focus on logic of operation codes by it self. Also this module contains 
declarations of auxiliary  date structures. There are declarations of data stack, 
call stack, list of labels and dictionary of frames. Dictionary of frames 
contain name of frame (GF/LF/TF) as keys and corresponding  objects to each frame. 
This objects are implemented in module \texttt{frames.py}

\subsubsection{Frames (\texttt{frames.py})}

Frames are implemented as objects with some polymorphic methods. This methods are: 
\texttt{get\_var}/\texttt{set\_var} for getting/setting variable from/to 
corresponding frame, \texttt{get\_frame} to getting whole frame with corresponding 
variables (in case of local frame this method returns frame from top of stack of 
local frames). Moreover in this module there is an implementation of data stack 
and methods for this.

\subsubsection{Error handling (\texttt{errors.py})}

Errors solved through exceptions. For each error which may arise in interpret 
there is class which inherits from python build-in objects Exception. This 
classes also provides custom log massages.  

\section{Testing}

Last part of this project is script for auto testing of parser, interpret and 
both of them together. 

\subsection{Program flow}

\subsubsection{Parameters hendling}

First of all script for testing checks input parameters: if there set 
\texttt{-{}-help} parameter, or if there is set custom interpret or parser 
script, set path to \texttt{jexamxml.jar} and so one. Also there is check for 
valid combinations of input parameters for script (\texttt{-{}-parse-only} can't 
be combined with \texttt{-{}-int-only}).

\subsubsection{Statiscis and HTML page}

After parameters control follows generating of HTML header to standart output. 
This header contains some CSS styles for beautifying page with statistics.  
Later during execution of test cases result of test would be formatted and 
written to corresponding string based on test success.   

\subsubsection{Collecting of test casses}

Before execution of tests, there is need to collect source files for each test 
cases. If flag \texttt{-{}-recursive} is set, then given directory will be 
discovered all files and subdirectories with \texttt{RecursiveIteratorIterator} 
class, otherwise with using of \texttt{DirectoryIterator} only files in given 
directory.

Collected files grouped to dictionaries with valid extension as keys and relative
path to test case (for example \texttt{[src] -> relative\_path.src}). Files 
grouped based on relative path, so files that corresponds to one test must have 
same path, otherwise assessment of test wouldn't be correct. 



\end{document}